\tool: Revisiting BadUSB with Type-C

### 2021-03-07 WOOT/Files/experiment.tex
fuck me with acronyms please

To evaluate the effectiveness of \tool in different modes, we conducted three
experiments on \tool using devices with USB Type-C capabilities from different
OEMs, including a mobile phone, a tablet, and a laptop.

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.

\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
%\fengwei{I think it is necessary to explain them in the text again.}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
	\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
	\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
	\end{tabular}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two USB Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victim's what mode should new screen be set to. \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a USB Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of Optical Character Recognition (OCR)  to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.4 (Build 18D52) with a USB Type-C interface, as the target
device in this experiment.  Besides disguising as normal HID devices like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

@@

Next, we summarize the possible threats toward user under different modes.
\hongyi{Better way to express this?}
First, under HID emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding OCR results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the OCR result with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized OCR result back to us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
In total, there are $94,058$ entries of data collected among 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expression are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

>>>>

To evaluate the effectiveness of \tool in different modes, we conducted three
experiments on \tool using devices with \ac{USB} Type-C capabilities from different
\acp{OEM}, including a mobile phone, a tablet, and a laptop.

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the \ac{HID} Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
with our modified firmware. About the \ac{USB} 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.

\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
%\fengwei{I think it is necessary to explain them in the text again.}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
	\circled[text=white,fill=myblue]{\footnotesize{1}} \ac{USB} 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
	\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
	\end{tabular}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victim's what mode should new screen be set to. \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a \ac{USB} Type-C interface, as the
target device.  In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker had
successfully extracted text like name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and perform transactions
without the password. As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

To test the capability of the full control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
device in this experiment.  Besides disguising as normal \acp{HID} like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

@@

Next, we summarize the possible threats toward user under different modes.
\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding \ac{OCR} results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the \ac{OCR} result with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized \ac{OCR} result back to us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are $94,058$ entries of data collected among 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expression are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

### 2021-03-07 WOOT/Files/introduction.tex
fuck me with acronyms please

The Universal Serial Bus (USB) protocol has become popular around the world
since its appearance, as it provides a unified and easy-to-use approach for a
large range of devices to communicate with each other.  From version 1.0 till
now, USB specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with USB support are ubiquitous.

On the other side of the coin, the security of USB has caused serious problems.
The designers of the USB protocol did not care much about security issues as
they wanted to make an easy-to-use protocol.  There are more than four hundred
vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of USB to conduct attacks, which puts
the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted through modification of the device firmware, which will disguise
normal USB devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typical simulated devices include HID (short for human interface
devices, including keyboards, mice, etc.) and disks.  Utilizing BadUSB,
attackers can pretend themselves as normal users, typing malicious commands to
victim computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily escape from traditional
anti-virus software since it is hard to distinguish them from normal USB
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers can not obtain the current user interface (UI) status which limits
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional UI patterns like buttons and links on victim
computers by disguising USB devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the usage of the host network.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of USB
2.0.  The release of USB 3.0 makes USB more powerful, with a higher
transmission rate for data and the support towards a larger range of
peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
can become more effective with the help of newly supported features in USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the USB device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of USB, named \tool.  \tool
extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional HIDs like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of USB attacks based on our approach to verify its effectiveness,
including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the USB devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated UI rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

@@

    \item To our best knowledge, this is the first work to utilize new features
	of USB Type-C.  The combination of new support with conventional BadUSB
	makes attacks more precise and effective.

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of USB specification.  Section~\ref{sec:related_work}
introduces the existing work of USB security from the aspects of attacking and
defense respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

>>>>

The \ac{USB} protocol has become popular around the world
since its appearance, as it provides a unified and easy-to-use approach for a
large range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

On the other side of the coin, the security of \ac{USB} has caused serious problems.
The designers of the \ac{USB} protocol did not care much about security issues as
they wanted to make an easy-to-use protocol.  There are more than four hundred
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted through modification of the device firmware, which will disguise
normal \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend themselves as normal users, typing malicious commands to
victim computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily escape from traditional
anti-virus software since it is hard to distinguish them from normal \ac{USB}
devices.

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers can not obtain the current \ac{UI} status which limits
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns like buttons and links on victim
computers by disguising \ac{USB} devices like mice.  That explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the usage of the host network.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a larger range of
peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.0.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID} like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

@@

    \item To our best knowledge, this is the first work to utilize new features
	of \ac{USB} Type-C.  The combination of new support with conventional BadUSB
	makes attacks more precise and effective.

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing work of \ac{USB} security from the aspects of attacking and
defense respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}
